\Large \includegraphics[height=\baselineskip]{title.png} \\ \vspace{0.65mm} \large \normalfont CSE 227: Computer Security - Spring 2017 \\ \textit{ University of California San Diego }

### 2017-06-12 docs/paper.tex
Review related work

% Authors
\author{
{\rm Chen Lai\footnote{Author names are ordered lexicographically, by last name.}}\\
\normalfont{\texttt{chl588@ucsd.edu}}
\and
{\rm Zhongrong Jian\footnotemark[\value{footnote}]}\\
\normalfont{\texttt{zhjian@ucsd.edu}}
\and
{\rm J. Sidrach\endnotemark[\value{endnote}]}\\
\normalfont{\texttt{jsidrach@ucsd.edu}}
}

@@

\section{Background}
TODO
- Browsers policy
- TLDs policy

@@

\begin{figure}[t]
  \includegraphics[width=\linewidth]{google.png}
  \includegraphics[width=\linewidth]{fakegoogle.png}
  \centering
  \caption{Google(top) and its homograph(bottom) on Chrome}
  \label{screenshot}
\end{figure}

\subsection{Browsers Policy}
The major browsers have their own IDN policies to defend against IDN homograph attack.
Google Chrome, starting with Chrome 51, will display Punycode if certain tests fail on the input URL.
These tests include but not limited to converting to Unicode, less than one numbering systems involved, no invisible characters, etc.
Internet Explorer\endnote{\url{https://support.microsoft.com/en-us/help/17621/internet-explorer-downloads}} displays URLs in IDN form if every component contains only characters from the languages configured in \textit{Internet Options}.
Firefox\endnote{\url{https://www.mozilla.org/en-US/firefox/new/}} uses a script mixing detection algorithm based on \textit{"Moderately Restrictive" profile of Unicode Technical Report 39} and displays Unicode when URL consists of any single script, any single script plus Latin, or it's in the white-list of other combinations.
Opera\endnote{\url{http://www.opera.com}} shows IDN only for whitelisted TLDs.
Safari\endnote{\url{https://www.apple.com/safari}} has a whitelist of scripts that do not contain confusable characters and only shows the IDN form for the whitelisted scripts.

\subsection{TLDs Policy}

\section{Related Work}
TODO
- Brief analysis of previous papers on the same topic

Many relevant studies have been conducted to show the vulnerability of IDN and provide possible solution to mitigate IDN homograph attack.

In 2001, Evgeniy Gabrilovich and Alex Gontmakher has proved the feasibility of such attack based on the vulnerability of Unicode in \textit{The Homograph Attack}~\cite{theHomoAttack}.

In 2006, Vicktor Krammer proposed a defense mechanism based on address bar highlighting/indication technique and better UI of the browsers~\cite{phishdefenseKV}.
His method of defense mainly target at regular users who do not neccessarily have relevant knowledge and through the better rendering of address along with explicit notification or alert on phishing url users would be aware of malicious website.
This method check each character in an URL separately, highlighting digits or characters of various scripts in different background color so that users will be aware of the difference.
It also suggest using larger font size in the address bar to help distinguish possible homograph characters from the Latin letter and alerting users when multi-script is detected by means of scripts block\endnote{\url{http://www.unicode.org/reports/tr24/}}.
His proposal was innovative in his year but not entirely accurate because characters from the same script may be in different blocks while characters from different scripts sometimes lie in the same block.

Manurer and Höfer believed that safe guard based on browsers' blacklist is far from enough to protect users from sophisticated phishing attacks~\cite{proc-eds-2012}.
They proposed an advanced method based on url components and spell checking functionality of search engine.
In this method, an url would be divided into several subterms, namely, base name\endnote{The primary domain name as registered at the registrar}, subdomain\endnote{A part of the primary domain}, path domain\endnote{A subfolder of the url}, brand name\endnote{A brand name that occurs in a url}.
Their algorithm is based on the following characteristics on different subterms of url:
\begin{itemize}
  \item Base name: Phisher cannot register the original domain but can only register mispelling or homograph domain name because the original one is often registered ahead by the company.
  \item Subdomain: Phisher can prepend subdomain to the primary domain being attacked to fool users into thinking that they are on the real domain. One example would be \url{http://us.battle.net.loginaccoutbattle.net/login/en/login.html}.
  \item Path domain: Phisher sometimes place a second domain as a subfolder of the url path, usually right after the primary domain name, for instance, \url{http://piasel.altervista.org/www.paypal.com/new/paypal/intl/update}.
  \item Brand name: There are cases that only the brand name is inserted somewhere in the URL to fool users.
\end{itemize}
Each of this components will be sent to search engine as a term for spelling check and in the cases that spelling suggestion is returned the url will be counted as suspicious.
By splitting a url into these subterms, this method cover almost all possible cases of fake url or domain name.
However, this mechanism is based on the search engine for return spelling suggestion and as a result, it does not perform well when it is used as sole detection.

@@

The manual classification sheds some light on how these homograph internationalized domain names are currently being used.
For the most part (82.34\%), the domains are registered by a third party, and not being used actively (parking).
One possible explanation for this is that the domain was bought in an attempt to be re-sold later at a higher price to the owner of the matching canonical homograph domain.
A detailed breakdown of this classification can be found in Table~\ref{manually-classified-idns}.

@@

\section{Conclusions}
TODO
- Conclusions of our work
- Possible future work
- TLDs

>>>>

% Authors
\author{
{\rm Chen Lai\footnote{Author names are ordered lexicographically, by last name.}}\\
\normalfont{\texttt{chl588@ucsd.edu}}
\and
{\rm Zhongrong Jian\footnotemark[\value{footnote}]}\\
\normalfont{\texttt{zhjian@ucsd.edu}}
\and
{\rm J. Sidrach\footnotemark[\value{footnote}]}\\
\normalfont{\texttt{jsidrach@ucsd.edu}}
}

@@

\section{Background}
TODO
- Introduction to the section, two mayor players in preventing the attack, different roles: browsers vs TLDs

\subsection{Browsers}
TODO
- Rewrite, browser by browser: chrome, firefox, edge, safari
- Significant changes in the past years?
- Not updated browsers/embedded browsers?
- Screenshot of two actual domains that look the same but are different
- Cut screenshots better

@@

\begin{figure}[t]
  \includegraphics[width=\linewidth]{images/google}
  \includegraphics[width=\linewidth]{images/fakegoogle-punycode}
  \centering
  \caption{Google(top) and its homograph(bottom) on Chrome}
  \label{screenshot}
\end{figure}

The major browsers have their own IDN policies to defend against IDN homograph attack.
Google Chrome, starting with Chrome 51, will display Punycode if certain tests fail on the input URL.
These tests include but not limited to converting to Unicode, less than one numbering systems involved, no invisible characters, etc.
Internet Explorer\endnote{\url{https://support.microsoft.com/en-us/help/17621/internet-explorer-downloads}} displays URLs in IDN form if every component contains only characters from the languages configured in \textit{Internet Options}.
Firefox\endnote{\url{https://www.mozilla.org/en-US/firefox/new/}} uses a script mixing detection algorithm based on \textit{"Moderately Restrictive" profile of Unicode Technical Report 39} and displays Unicode when URL consists of any single script, any single script plus Latin, or it's in the white-list of other combinations.
Opera\endnote{\url{http://www.opera.com}} shows IDN only for whitelisted TLDs.
Safari\endnote{\url{https://www.apple.com/safari}} has a whitelist of scripts that do not contain confusable characters and only shows the IDN form for the whitelisted scripts.

\subsection{Top-Level Domains}
TODO
- What does different TLDs do
- ccTLDs

\section{Related Work}
Several relevant studies have been conducted to describe the potential security issues with internationalized domain names, while providing possible solutions to mitigate the surface attack of these homograph domain names. The first of these studies, \textit{The Homograph Attack}~\cite{gabrilovich2002}, was written by Evgeniy Gabrilovich and Alex Gontmakher in 2001, and proved the feasability of the attack.

In 2006, Vicktor Krammer proposed a defense mechanism based on address bar highlighting on the browsers and a better user interface~\cite{krammer2006}.
This method of defense mainly targets regular users, by making them explicitly aware of the URL differences.
It checks each character in a URL separately, highlighting digits or characters of various scripts in different background colors, so that users can easily tell the difference.
It also suggests using larger font sizes in the address bar, to help distinguish possible homograph characters from their Latin counterparts.

In 2012, Maurer and H\"{o}fer argued that safe-guards based on browsers' blacklists was far from enough to protect users from sophisticated phishing attacks~\cite{maurer2012}.
They proposed a more complex method based on URL components and the spell checking functionality of any search engine.
In this method, a URL is be divided into several parts, namely, base name (the primary domain name as registered at the registrar), sub-domain (part before the primary domain, i.e., before the last identifier and TLD), path domain (sub-folder of the URL), and brand name (any popular brand name that is present in the URL).
Their algorithm tries to prevent the attack by analyzing each of these URL parts.
Each one is sent to the search engine for a spelling check, and in the cases that a spelling suggestion is returned, the URL will be marked as suspicious.
By splitting the URL into these parts, this method aims to cover almost all possible cases of confusable URLs or domain names.
However, this mechanism relies exclusively on the search engine to return spelling suggestions, and as a result, it is highly dependent on the search engine and query itself.

While these last two methods were not adopted, they have influenced other possible mitigations currently implemented in most modern browsers.
For instance, the base name of the URL is displayed in a darker color in Google Chrome and Mozilla Firefox.
Safari goes a step further and only shows the base name of the URL.

Other attempts to analyze the impact of homograph attacks have also been made.
In 2009, Peter Hanay and Christopher Bolan~\cite{hannay2009} concluded that, while most modern browsers in fact have implemented useful measures to prevent internationalized domain name homograph attacks, email clients where not nearly as effective, specially when dealing with incoming emails.
In 2010, Johnny Al Helou and Scott Tilley~\cite{al2010} argued that the introduction of country-code Top Level Domains (ccTLDs) have made this attack easier to perform again.

Our approach to analyze the potential security risk of homograph internationalized domain names was fundamentally different the ones evaluated.
Rather than inspecting traffic or generating random homograph permutations of a string, we took a more systematic approach.
We clustered all internationalized homograph domains using a snapshot of the \texttt{.com} domain zone.
We then used a list of top web sites and domain registrants data to classify each homograph domain name.

@@

The manual classification sheds some light on how these homograph internationalized domain names are currently being used.
For the most part (82.34\%), the domains are registered by a third party, and not being used actively (parking).
One possible explanation for this is that the domain was bought in an attempt to be re-sold later at a higher price to the owner of the matching canonical homograph domain.
However, the potential security risk is still present as there are no guarantees that the parked domains will remain inactive in the future.
A detailed breakdown of this classification can be found in Table~\ref{manually-classified-idns}.

@@

\section{Conclusions}
TODO
- Conclusions of our work
- Possible future work
- TLDs
- Hard to balance (rendering idn useless vs preventing the attack)
